%!TEX root = cv.tex

\newcommand{\pdflink}[1]{\href{https://artemyk.github.io/assets/pdf/papers/#1.pdf}{pdf}}
\newcommand{\publink}[1]{\href{#1}{link}}

P.M. Riechers, C. Gupta, \textbf{A. Kolchinsky}, M. Gu, ``Thermodynamically ideal quantum state inputs to any device'', \emph{PRX Quantum}, 2024. \pdflink{Riechers_2024_ThermodynamicallyIdealInputs} \publink{https://journals.aps.org/prxquantum/abstract/10.1103/PRXQuantum.5.030318}

\textbf{A. Kolchinsky}, ``Partial information decomposition: redundancy as information bottleneck'', \emph{Entropy}, 2024. \pdflink{Kolchinsky_2024_PIDasIB} \publink{https://www.mdpi.com/1099-4300/26/7/546}

J. Piñero, R. Solé, \textbf{A. Kolchinsky}, ``Optimization of nonequilibrium free energy harvesting illustrated on bacteriorhodopsin'', \emph{Physical Review Research}, 2024. \pdflink{Pinero_Sole_Kolchinsky_2024_OptimizationOfFreeEnergyHarvesting} \publink{https://journals.aps.org/prresearch/abstract/10.1103/PhysRevResearch.6.013275}

\textbf{A. Kolchinsky}, N. Ohga, S. Ito, ``Thermodynamic bound on spectral perturbations, with applications to oscillations and relaxation dynamics'', \emph{Physical Review Research}, 2024. \pdflink{Kolchinsky_Ohga_Ito_ThermodynamicBoundOnSpectralPerturbations} \publink{https://journals.aps.org/prresearch/pdf/10.1103/PhysRevResearch.6.013082}

D.R. Sowinski, J. Carroll-Nellenback, R.N. Markwick, J. Piñero, M. Gleiser, \textbf{A. Kolchinsky}, G. Ghoshal, A. Frank, ``Semantic Information in a model of resource gathering agents'', \emph{PRX Life}, 2023. \pdflink{Sowinski-SemanticInformationInAModelOfResourceGatheringAgents} \publink{https://journals.aps.org/prxlife/abstract/10.1103/PRXLife.1.023003}

\textbf{A. Kolchinsky}, ``Generalized Zurek's bound on the cost of an individual classical or quantum computation'', \emph{Physical Review E}, 2023. \pdflink{Kolchinsky_2023_GeneralizedZureksBound} \publink{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.108.034101}

M. Aguilera and \textbf{A. Kolchinsky}, ``Quantifying higher-order entropy production in organized nonequilibrium states'', \emph{Proceedings of the ALIFE 2023}, 2023. \pdflink{Aguilera_2023_QuantifyingHigherOrderEP} \publink{https://direct.mit.edu/isal/proceedings/isal/35/45/116909}

N. Ohga, S. Ito, \textbf{A. Kolchinsky}, ``Thermodynamic bound on the asymmetry of cross-correlations'', \emph{Physical Review Letters}, 2023. (\emph{Editors' Suggestion}; \emph{Featured in \href{https://physics.aps.org/articles/v16/142}{Physics}}) \pdflink{Ohga_Ito_Kolchinsky_2023_ThermodynamicBoundOnTheAsymmetryOfCrossCorrelations} \publink{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.131.077101}

K. Yoshimura, \textbf{A. Kolchinsky}, A. Dechant, S. Ito, ``Housekeeping and excess entropy production for general nonlinear dynamics'', 
\emph{Physical Review Research}, 2023. \pdflink{Yoshimura_PRR_2023} \publink{https://journals.aps.org/prresearch/abstract/10.1103/PhysRevResearch.5.013017}

F.C. Sheldon, \textbf{A. Kolchinsky}, F. Caravelli, ``Computational capacity of LRC, memristive, and hybrid reservoirs'', \emph{Physical Review E}, 2022. \pdflink{Sheldon_LRC_PRE_2022} \publink{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.106.045310}

\textbf{A. Kolchinsky}, ``A Novel Approach to the Partial Information Decomposition'', \emph{Entropy}, 2022.
\pdflink{Kolchinsky_2022_Novel_Approach_to_the_PID} \href{https://github.com/artemyk/redundancy}{code} \publink{https://www.mdpi.com/1099-4300/24/3/403}

\textbf{A. Kolchinsky} and D.H. Wolpert, ``Dependence of integrated, instantaneous, and fluctuating entropy production on the initial state in quantum and classical processes'', \emph{Physical Review E}, 2021. \pdflink{Kolchinsky_Wolpert_2021_Mismatch_cost} \publink{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.104.054107}

\textbf{A. Kolchinsky} and D.H. Wolpert, ``Work, entropy production, and thermodynamics of information under protocol constraints'', \emph{Physical Review X}, 2021. \pdflink{Kolchinsky_Wolpert_2021_PRX_Constraints} \publink{https://journals.aps.org/prx/abstract/10.1103/PhysRevX.11.041024}

\textbf{A. Kolchinsky} and D.H. Wolpert, ``Entropy production given constraints on the energy functions'', \emph{Physical Review E}, 2021. \pdflink{Kolchinsky and Wolpert - 2021 - Entropy production given constraints on the energy functions} \publink{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.104.034129}

\textbf{A. Kolchinsky} and D.H. Wolpert, ``Thermodynamic costs of Turing Machines'', \emph{Physical Review Research}, 2020. % 2(3), 033312,  August 2020
\pdflink{Kolchinsky_Wolpert_2020_Thermodynamic costs of Turing machines} \publink{https://journals.aps.org/prresearch/abstract/10.1103/PhysRevResearch.2.033312}

D.H. Wolpert and \textbf{A. Kolchinsky}, ``The thermodynamics of computing with circuits'', \emph{New Journal of Physics}, 2020.  % 22, 063047, June 2020
\pdflink{Wolpert and Kolchinsky - 2020 - Thermodynamics of computing with circuits} \publink{https://iopscience.iop.org/article/10.1088/1367-2630/ab82b8/meta}

\textbf{A. Kolchinsky} and B. Corominas-Murtra, ``Decomposing information into copying versus transformation'', 
\emph{Royal Society Interface}, 2020. % 17(162), 20190623,  January 2020
\pdflink{Kolchinsky_Corominas-Murtra_2020_Decomposing information into copying versus transformation} \publink{https://royalsocietypublishing.org/doi/full/10.1098/rsif.2019.0623}

A.M. Saxe, Y. Bansal, J. Dapello, M. Advani, \textbf{A. Kolchinsky}, B.D. Tracey, D.D. Cox, 
``On the information bottleneck theory of deep learning'',  \emph{Journal of Statistical Mechanics}, 2019. 
\pdflink{Saxe et al_2019_On the information bottleneck theory of deep learning} 
\href{https://github.com/artemyk/ibsgd/tree/iclr2018}{code} \publink{https://iopscience.iop.org/article/10.1088/1742-5468/ab3985/meta} % 124020, Dec 2019

\textbf{A. Kolchinsky}, B.D. Tracey, D.H. Wolpert, ``Nonlinear information bottleneck'', \emph{Entropy}, 2019.
 (\href{https://www.mdpi.com/journal/entropy/awards/1209}{{\emph{Entropy} 2021 Best Paper Award}}) \pdflink{Kolchinsky et al_2019_Nonlinear information bottleneck} \publink{https://www.mdpi.com/1099-4300/21/12/1181}

A. Berdahl, C. Brelsford, C. De Bacco, M. Dumas, V. Ferdinand, J.A. Grochow, L. Hébert-Dufresne,
Y. Kallus, C.P. Kempes, \textbf{A. Kolchinsky}, D. B. Larremore,
E. Libby, E.A. Power, C.A. Stern, B.D.Tracey, ``Dynamics of beneficial epidemics'', \emph{Scientific Reports}, 2019. 
\pdflink{Berdahl et al_2019_Dynamics of beneficial epidemics} \publink{https://www.nature.com/articles/s41598-019-50039-w}

E.A. Hobson, V. Ferdinand, \textbf{A. Kolchinsky}, J. Garland, 
``Rethinking animal social complexity measures with the help of complex systems concepts'', 
\emph{Animal Behaviour}, 2019. 
\pdflink{Hobson et al_2019_Rethinking animal social complexity measures with the help of complex systems} \publink{https://www.sciencedirect.com/science/article/pii/S0003347219301666}

\textbf{A. Kolchinsky}, B.D. Tracey, S. Van Kuyk, ``Caveats for information bottleneck in deterministic scenarios'', \emph{International Conf on Learning Representations (ICLR)}, 2019. 
\pdflink{Kolchinsky et al_2019_Caveats for information bottleneck in deterministic scenarios} 
\href{https://github.com/artemyk/ibcurve}{code} \publink{https://openreview.net/forum?id=rke4HiAcY7}

D.H. Wolpert, \textbf{A. Kolchinsky}, J.A. Owen, ``A space–time tradeoff for implementing a function with master equation dynamics'', \emph{Nature Communications}, 2019. 
\pdflink{Wolpert et al_2019_A space–time tradeoff for implementing a function with master equation dynamics} \publink{https://www.nature.com/articles/s41467-019-09542-x}

A. Avena-Koenigsberger, X. Yan, \textbf{A. Kolchinsky}, M. van den Heuvel, P. Hagmann, O. Sporns, 
``A spectrum of routing strategies for brain networks'', \emph{PLoS Computational Biology}, 2019. 
\pdflink{Avena-Koenigsberger et al_2019_A spectrum of routing strategies for brain networks} \publink{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006833}

J.A. Owen, \textbf{A. Kolchinsky}, D.H. Wolpert, ``Number of hidden states needed to physically implement a given conditional distribution'', \emph{New Journal of Physics}, 2019. (\href{https://iopscience.iop.org/article/10.1088/1367-2630/ab60f8}{correction}) 
\pdflink{Owen et al_2018_Number of hidden states needed to physically implement a given conditional} \publink{https://iopscience.iop.org/article/10.1088/1367-2630/aaf81d/meta}

\textbf{A. Kolchinsky} and D.H. Wolpert, 
``Semantic information, autonomous agency, and nonequilibrium statistical physics'', 
\emph{Royal Society Interface Focus}, 2018. 
\pdflink{Kolchinsky_Wolpert_2018_Semantic information, autonomous agency and non-equilibrium statistical physics} 
\href{https://github.com/artemyk/semantic_information/}{code} \publink{https://royalsocietypublishing.org/doi/full/10.1098/rsfs.2018.0041}

A.M. Saxe, Y. Bansal, J. Dapello, M. Advani, \textbf{A. Kolchinsky}, B.D. Tracey, D.D. Cox, 
``On the information bottleneck theory of deep learning'', \emph{International Conf on Learning Representations (ICLR)}, 2018. 
\pdflink{Saxe et al_2018_ICLR} \href{https://github.com/artemyk/ibsgd/tree/iclr2018}{code} \publink{https://openreview.net/forum?id=ry_WPG-A-}

\textbf{A. Kolchinsky}, N. Dhande, K. Park, Y.Y. Ahn, ``The Minor Fall, the Major Lift: Inferring emotional valence of musical chords through lyrics'', \emph{Royal Society Open Science}, 2017. 
\pdflink{Kolchinsky et al_2017_The Minor fall, the Major lift} 
\href{https://doi.org/10.6084/m9.figshare.5413060.v1.}{data} 
\href{https://github.com/artemyk/chordsentiment}{code} \publink{https://royalsocietypublishing.org/doi/full/10.1098/rsos.170952}

\textbf{A. Kolchinsky}, D.H. Wolpert, ``Dependence of dissipation on the initial distribution over states'',
\emph{Journal of Statistical Mechanics}, 2017. 
\pdflink{Kolchinsky_Wolpert_2017_Dependence of dissipation on the initial distribution over states} \publink{https://iopscience.iop.org/article/10.1088/1742-5468/aa7ee1/meta} 

\textbf{A. Kolchinsky}, B.D. Tracey, ``Estimating mixture entropy with pairwise distances'', \emph{Entropy}, 2017.
(\href{https://www.mdpi.com/1099-4300/19/11/588}{correction}) 
\pdflink{Kolchinsky_Tracey_2017_Estimating Mixture Entropy with Pairwise Distances} 
\href{https://github.com/btracey/mixent/}{code} \publink{https://www.mdpi.com/1099-4300/19/7/361}


\textbf{A. Kolchinsky}, A.J. Gates, L.M. Rocha, ``Modularity and
the spread of perturbations in complex dynamical systems,'' \emph{Physical Review E}, 2015. 
\pdflink{Kolchinsky et al_2015_Modularity and the spread of perturbations in complex dynamical systems}
\href{https://github.com/artemyk/perturbationmodularity/}{code} \publink{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.92.060801}

\textbf{A. Kolchinsky}, A. Lourenço, H. Wu, L. Li, L.M. Rocha,
``Extraction of pharmacokinetic evidence of drug-drug interactions
from the literature,'' \emph{PLOS One}, 2015. 
\pdflink{Kolchinsky et al_2015_Extraction of Pharmacokinetic Evidence of Drug–Drug Interactions from the} \publink{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0122199}

\textbf{A. Kolchinsky}, M.P. van den Heuvel, A. Griffa, P. Hagmann, L.M. Rocha, O. Sporns, J. Goñi, ``Multi-scale
integration and predictability in resting state brain activity,'' 
\emph{Frontiers in Neuroinformatics}, 2014. 
\pdflink{Kolchinsky et al_2014_Multi-scale integration and predictability in resting state brain activity} \publink{https://www.frontiersin.org/articles/10.3389/fninf.2014.00066/full}

A. Rossi, F.J. Parada, \textbf{A. Kolchinsky}, A. Puce, ``Neural correlates of apparent motion perception of impoverished facial stimuli I: A comparison of ERP and ERSP activity,'' \emph{NeuroImage}, 2014. 
\pdflink{Rossi et al_2014_Neural correlates of apparent motion perception of impoverished facial stimuli} \publink{https://www.sciencedirect.com/science/article/pii/S1053811914002845}

\textbf{A. Kolchinsky}, A. Lourenço, L. Li, L.M. Rocha, ``Evaluation of linear classifiers on articles containing pharmacokinetic evidence of drug-drug interactions,'' \emph{Proc Pacific Symposium on Biocomputing}, 2013. 
\pdflink{Kolchinsky et al_2013_Evaluation of linear classifiers on articles containing pharmacokinetic} \publink{https://www.worldscientific.com/doi/abs/10.1142/9789814447973_0040}

\textbf{A. Kolchinsky} and L.M. Rocha, ``Prediction and modularity in dynamical systems,'' \emph{Proc
of European Conf. on the Synthesis and Simulation of Living Systems (ECAL)}, 2011. 
\pdflink{Kolchinsky_Rocha_2011_Prediction and modularity in dynamical systems} \publink{https://direct.mit.edu/isal/proceedings/ecal2011/23/65/111139}

\textbf{A. Kolchinsky}, A. Abi-Haidar, J. Kaur, A.A. Hamed, L.M. Rocha, ``Classification of protein-protein interaction full-text documents using text and citation network features,'' \emph{IEEE/ACM Transactions on Computational Biology and Bioinformatics}, 2010. 
\pdflink{Kolchinsky et al_2010_Classification of Protein-Protein Interaction Full-Text Documents Using Text} \publink{https://dl.acm.org/doi/10.1109/TCBB.2010.55}

